\subsection{Document goal}
The purpose of this document is to provide all the necessary information to extend, correct and improve Colletta.
There will be additional information regarding setting up the development environment to work in an environment that is as consistent as possible with that used
by the other members of group SWEight, but can be ignored if you only want to use part of the product.
This guide was written taking into account the Microsoft Windows and Linux operating systems. If other systems are used, compatibility issues may arise, even if it's unlikely. In this case refer to the git page. This document will grow as the product will be fully
developed.

\subsection{Product goal}
The purpose of the product is the creation of a collaborative data collection platform where users can prepare and/or perform small grammar exercises. 
The front-end of the system consists of a web application developed with React and Redux, while the back-end is a Spring Boot application written in Java, which will handle HTTP Requests sent from the front-end. 

\subsection{References}


\subsubsection{Installation references}

\begin{itemize}
\item \textbf{Git}: \url{https://git-scm.com/}
\item \textbf{Node.js}: \url{https://nodejs.org/en/}
\item \textbf{NPM}: \url{https://www.npmjs.com/}
\item \textbf{Oracle JDK}: \url{https://www.oracle.com/technetwork/java/javase/downloads/index.html}
\item \textbf{OpenJDK}: \url{https://openjdk.java.net/}
\item \textbf{Maven}: \url{https://maven.apache.org/}
\item \textbf{Lombok}: \url{https://projectlombok.org/}
\item \textbf{VSCode}: \url{https://code.visualstudio.com/} 

\end{itemize}

\subsubsection{Legal references}
\begin{itemize}
\item \textbf{MIT License}: \url{https://opensource.org/licenses/MIT}
\end{itemize}

%\subsubsection{Informative references}
